---
title: "DBDF-FTC incubations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      collapse = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      comment = "#>"
                      )
```

## "Repeated freeze-thaw cycles increase extractable, but not total, carbon and nitrogen in a Maine coniferous soil"


### Experiment

O and B horizon soils were collected from the Dwight B. Demerritt Forest. Sieved (6 mm/2 mm) and homogenized.  
The soil was weighed into Mason jars and subjected to one of four treatments (experimental replication n = 5):

1. FTC-1: frozen continuously with one 24-hour thaw period
1. FTC-2: frozen continuously with two 24-hour thaw periods
1. FTC-6: frozen continuously with six 24-hour thaw periods
1. control: continuously kept at +5 C

Incubations lasted 6 weeks (42 days) total.

Frozen conditions were -10 C, thaw conditions were +5 C

Subsamples were collected from the soils before and after the incubation, for chemistry analysis.

Respiration (CO2 flux) was measured on all samples before and after the incubation, and on FTC-6 soils during a few thaw periods. 
The jars were sealed for 60 minutes, and 10-mL headspace samples were collected with a syringe at 0, 20, 40, 60 minute intervals.


### Results

**Total C, total N**

```{r tctn_graph, fig.height=4, fig.width=7}
readd(tctn_graphs)
```

**Extractable NH4-N**

```{r nh4_graph, fig.height=4, fig.width=7}
readd(nh4_graph)
```

**Water extractable organic C**

```{r weoc_graphs, fig.height=4, fig.width=7}
readd(weoc_graphs)
```

**Respiration**

```{r resp_graphs, fig.height=4, fig.width=7}
readd(respiration_graphs)$gg_resp
```

Temporal changes in respiration for FTC-6 and control soils, measured during the thaw periods

```{r resp_graphs2, fig.height=5, fig.width=7}
readd(respiration_graphs)$gg_resp_ftc6
```

---

<details>   
   <summary>Session Info</summary>
   
Date run: `r `Sys.Date()`

```{r}
sessionInfo()
```

</details> 